---
title: "Biol 801/Evrn 420/720, Example of unit testing using fake genetic data, unit tests"
date: "March 2018"
output: 
  pdf_document:
    highlight: tango
fontsize: 11pt
geometry: margin=1in

documentclass: article
---

# Tests for find_fixed

```{r find_fixed_source, echo=T}
source("find_fixed.R")
```

This is a low-level function, so let's start with it. 

Test it can find one length-2 pattern by itself:

```{r find_fixed_test_1, echo=T}
ms<-"AT"
seq<-"CGAAGGCTATAGA"
h<-find_fixed(ms,seq)
if (length(h)==1 && h==9)
{
  print("passed")
} else
{
  print("failed")
}
```

Test it can find a length-4 pattern by itself:

```{r find_fixed_test_2, echo=T}
ms<-"ATGG"
seq<-"AGCTTATGGAAGGCC"
h<-find_fixed(ms,seq)
if (length(h)==1 && h==6)
{
  print("passed")
} else
{
  print("failed")
}
```

Test if output is appropriate if the pattern repeats:

```{r find_fixed_test_3, echo=T}
ms<-"AG"
seq<-"TGACCAGAGAGATCCGGGG"
h<-find_fixed(ms,seq)
if (length(h)==3 && sum(h==c(6,8,10))==3)
{
  print("passed")
} else
{
  print("failed")
}
```

What if ms itself has a repeat?

```{r find_fixed_test_4, echo=T}
ms<-"AGAG"
seq<-"ATGGCAACAGAGAGAGCCGTAGTC"
h<-find_fixed(ms,seq)
if (length(h)==3 && sum(h==c(9,11,13))==3)
{
  print("passed")
} else
{
  print("failed")
}
```

Note this helps us with our design - the output here is of length 3, whereas it
would have been of length 2 for a non-repeating `ms`, and we will have to be aware 
of this when writing `find_repeat`.

# Tests for my_find_fixed functioin from find_fixed.R file

```{r my_find_fixed_test1}
ms<-"AG"
seq<-"TAGAGTCAGCCTAGag"
h<-my_find_fixed(ms=ms,seq=seq)
if(length(h)==4 && all(h==c(2,4,8,13))==T){
  print("my_find_fixed_test1 : passed")
}else{
  print("my_find_fixed_test1 : failed")
}
```

```{r my_find_fixed_test2}
ms<-"AGAG" # What if ms itself has a repeat?
seq<-"TAGAGTCAGCCTAGagAGAGTCAGAG"
h<-my_find_fixed(ms=ms,seq=seq)
if(length(h)==3 && all(h==c(2,17,23))==T){
  print("my_find_fixed_test2 : passed")
}else{
  print("my_find_fixed_test2 : failed")
}
```

# Tests for getseqs

```{r getseqs_source, echo=T}
source("getseqs.R")
```

This is another low-level function, so let's continue with it next.

I realized I could make my best implementation of `getseqs` using the function `dec_to_baseb` which converts a nonnegative decimal integer into its base-b equivalent. Test it for a few examples:

```{r baseb_test_1, echo=T}
h<-dec_to_baseb(12,4)
if (length(h)==2 && sum(h==c(3,0))==2)
{
  print("passed")
} else
{
  print("failed")
}
h<-dec_to_baseb(320,4)
if (length(h)==5 && sum(h==c(1,1,0,0,0))==5)
{
  print("passed")
} else
{
  print("failed")
}
```

We already thought of this one at the design stage:

```{r getseqs_test_1, echo=T}
h<-getseqs(2)
if (length(h)==4^2 && sum(h==c("AA", "AC", "AG", "AT", "CA", "CC", "CG", "CT", "GA", "GC", "GG", "GT", "TA", "TC", "TG", "TT"))==4^2)
{
  print("passed")
} else
{
  print("failed")
}
```

Note we also realize something here of which we should remain aware: repeating patterns are included!

Simple test for length-4 patterns, only tests the length because I do not want to type out all $4^4=256$ length-4 sequences:

```{r getseqs_test_2, echo=T}
h<-getseqs(4)
if (length(h)==4^4)
{
  print("passed")
} else
{
  print("failed")
}
```

# Tests for find_repeat

```{r find_repeat_source, echo=T}
source("find_repeat.R")
```

Test for one repeat of the target `ms` only: 

```{r find_repeat_test_1, echo=T}
ms<-"CG"
seq<-"AATGGGCCACGCGCGCGCGCGCGCGCGCGCGACAATTCGCGCGCGGA"
#Note this has CG occuring 4 times (which should be ignored) as well as 11 times
repmin<-10  
h<-find_repeat(ms,seq,repmin)
#should be one row with 11 reps at start loc 10
if(dim(h)[1]==1)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="CG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==10)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==11)
{
  print("passed")
} else
{
  "failed"
}
```

Test for two repeats:

```{r find_repeat_test_2, echo=T}
ms<-"CG"
seq<-"AATGGGCCACGCGCGCGCGCGCGCGCGCGCGACAATTCGCGCGCGGA"
#Note this has CG occuring 4 times (which should be ignore) as well as 11 times
repmin<-4  
h<-find_repeat(ms,seq,repmin)
#should be two rows, one with 11 reps at start loc 10, one with 4 reps at loc 38 
if(dim(h)[1]==2)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="CG" && h[2,1]=="CG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==10)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==11)
{
  print("passed")
} else
{
  "failed"
}
if (h[2,2]==38)
{
  print("passed")
} else
{
  "failed"
}
if (h[2,3]==4)
{
  print("passed")
} else
{
  "failed"
}
```

Test for the case of an `ms` that itself has repeats. This is a test written in response to something we realized 
in our above unit testing. We will have to write the function to get this right.

```{r find_repeat_test_3, echo=T}
ms<-"AGAG"
seq<-"TTAGAGAGAGAGAGAGAGAGAGTTACACT"
repmin<-4
h<-find_repeat(ms,seq,repmin)
if(dim(h)[1]==1)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="AGAG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==3)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==5)
{
  print("passed")
} else
{
  "failed"
}
```

# Tests for find_microsats

```{r find_microsats_source, echo=T}
source("find_microsats.R")
```

Test for an example with various features but little else between the features:

```{r }
seq<-paste0("T", #pos 1
            "AGAGAGAG", #pos 2 to 9, 4 reps of AG, 3 reps of GA
            "T", #pos 10
            "CATCATCATCATCAT", #pos 11 to 25, 5 reps of CAT, 5 reps of ATC, 5 reps of TCA
            "CTT", #pos 26 to 28
            "AGAGAGAGAGAGAGAG", #pos 29 to 44, 8 reps of AG, 8 reps of GA (including subsequent A)
            "ATC", #pos 45 to 47
            "AAAAAAAA", #pos 48 to 55, 4 reps of AA,  
            "TTA")
h<-find_microsats(seq=seq,lenmin=2,lenmax=6,repmin=4)
h
```

The result should show:  

- 4 reps of "AG" starting at pos 2
- 5 reps of "CAT" starting at pos 11
- 5 reps of "ATC" starting at 12
- 5 reps of "TCA" starting at 10
- 8 reps of "AG" starting at pos 29
- 8 reps of "GA" starting at pos 30
- 4 reps of "AA" starting at pos 48
- 4 reps of "AGAG" starting at pos 29
- 4 reps of "GAGA" starting at pos 30

I don't care what order these appear in.


We should get the abovesaid result if my written function is correct. To test that:
```{r }
seq<-paste0("T", #pos 1
            "AGAGAGAG", #pos 2 to 9, 4 reps of AG, 3 reps of GA
            "T", #pos 10
            "CATCATCATCATCAT", #pos 11 to 25, 5 reps of CAT, 5 reps of ATC, 5 reps of TCA
            "CTT", #pos 26 to 28
            "AGAGAGAGAGAGAGAG", #pos 29 to 44, 8 reps of AG, 8 reps of GA (including subsequent A)
            "ATC", #pos 45 to 47
            "AAAAAAAA", #pos 48 to 55, 4 reps of AA,  
            "TTA")
h<-my_find_microsats(seq=seq,lenmin=2,lenmax=6,repmin=4) # it's a data-frame
h_mat<-as.matrix(h)
h_mat <- h_mat[order(h_mat[,1]),] # it's a matrix now : sorted as alphabetically ms in 1st column
h_mat
```











