---
title: "Biol 801/Evrn 420/720, Example of unit testing using fake genetic data, unit tests"
date: "March 2018"
output: 
  pdf_document:
    highlight: tango
fontsize: 11pt
geometry: margin=1in

documentclass: article
---

# Tests for find_fixed
This is a low-level function, so let's start with it. 

Test it can find one length-2 pattern by itself:

```{r find_fixed_test_1, echo=T}
ms<-"AT"
seq<-"CGAAGGCTATAGA"
h<-find_fixed(ms,seq)
if (length(h)==1 && h==9)
{
  print("passed")
} else
{
  print("failed")
}
```

Test it can find a length-4 pattern by itself:

```{r find_fixed_test_2, echo=T}
ms<-"ATGG"
seq<-"AGCTTATGGAAGGCC"
h<-find_fixed(ms,seq)
if (length(h)==1 && h==6)
{
  print("passed")
} else
{
  print("failed")
}
```

Test if output is appropriate if the pattern repeats:

```{r find_fixed_test_3, echo=T}
ms<-"AG"
seq<-"TGACCAGAGAGATCCGGGG"
h<-find_fixed(ms,seq)
if (length(h)==3 && sum(h==c(6,8,10))==3)
{
  print("passed")
} else
{
  print("failed")
}
```

What if ms itself has a repeat?

```{r find_fixed_test_4, echo=T}
ms<-"AGAG"
seq<-"ATGGCAACAGAGAGAGCCGTAGTC"
h<-find_fixed(ms,seq)
if (length(h)==3 && sum(h==c(9,11,13))==3)
{
  print("passed")
} else
{
  print("failed")
}
```

Note this helps us with our design - the output here is of length 3, whereas it
would have been of length 2 for a non-repeating `ms`, and we will have to be aware 
of this when writing `find_repeat`.

# Tests for getseqs
This is another low-level function, so let's continue with it next.

We already thought of this one at the design stage:

```{r getseqs_test_1, echo=T}
h<-getseqs(2)
if (length(h)==4^2 && sum(h==c("AA", "AC", "AG", "AT", "CA", "CC", "CG", "CT", "GA", "GC", "GG", "GT", "TA", "TC", "TG", "TT"))==4^2)
{
  print("passed")
} else
{
  print("failed")
}
```

Note we also realize something here of which we should remain aware: repeating patterns are included!

Simple test for length-4 patterns, only tests the length because I do not want to type out all $4^4=256$ length-4 sequences:

```{r getseqs_test_2, echo=T}
h<-getseqs(4)
if (length(h)==4^4)
{
  print("passed")
} else
{
  print("failed")
}
```

# Tests for find_repeat

Test for one repeat of the target `ms` only: 

```{r find_repeat_test_1, echo=T}
ms<-"CG"
seq<-"AATGGGCCACGCGCGCGCGCGCGCGCGCGCGACAATTCGCGCGCGGA"
#Note this has CG occuring 4 times (which should be ignored) as well as 11 times
repmin<-10  
h<-find_repeat(ms,seq,repmin)
#should be one row with 11 reps at start loc 10
if(dim(h)[1]==1)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="CG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==10)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==11)
{
  print("passed")
} else
{
  "failed"
}
```

Test for two repeats:

```{r find_repeat_test_2, echo=T}
ms<-"CG"
seq<-"AATGGGCCACGCGCGCGCGCGCGCGCGCGCGACAATTCGCGCGCGGA"
#Note this has CG occuring 4 times (which should be ignore) as well as 11 times
repmin<-4  
h<-find_repeat(ms,seq,repmin)
#should be two rows, one with 11 reps at start loc 10, one with 4 reps at loc 38 
if(dim(h)[1]==2)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="CG" && h[2,1]=="CG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==10)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==11)
{
  print("passed")
} else
{
  "failed"
}
if (h[2,2]==38)
{
  print("passed")
} else
{
  "failed"
}
if (h[2,3]==4)
{
  print("passed")
} else
{
  "failed"
}
```

Test for the case of a `ms` that itself has repeats. This is a test written in response to something we realized 
in our above unit testing. We will have to write the function to get this right.

```{r find_repeat_test_3, echo=T}
ms<-"AGAG"
seq<-"TTAGAGAGAGAGAGAGAGAGAGTTACACT"
repmin<-4
h<-find_repeat(ms,seq,repmin)
if(dim(h)[1]==1)
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,1]=="AGAG")
{
  print("passed")
} else
{
  print("failed")
}
if (h[1,2]==3)
{
  print("passed")
} else
{
  "failed"
}
if (h[1,3]==5)
{
  print("passed")
} else
{
  "failed"
}
```

# Tests for find_microsats

Test for an example with various features but little else between the features:

```{r }


```